A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-01-30 analysis/paper/paper.Rmd
dont need to include libs

# Discussion
# Conclusion

# Online Methods

@@

We gathered a list of `r sum(methods$is_ti, na.rm=TRUE)` trajectory inference methods `r ref("table", "methods", anchor=TRUE)`, based on two existing lists found online [@davis_awesomesinglecelllistsoftware_2018,@gitter_singlecellpseudotimeoverviewalgorithms_2018] and by searching in literature for "trajectory inference" and "pseudotemporal ordering". We believe this to be the most complete list to data, but are happy to include additional methods through e-mail or an issue on our github (https://github.com/dynverse/dynalysis). Methods were excluded from the evaluation based on several criteria: `r glue::collapse(glue::glue("({non_inclusion_reasons$footnote}) {non_inclusion_reasons$long}"), ", ")`. This resulted in the inclusion of `r sum(methods$evaluated)` methods in the evaluation (`r ref("table", "methods")`).

@@

We created a transparent scoring scheme to check the quality of each method (`r ref("table", "methods")`) and used several references to weigh each quality check.

>>>>

# Discussion

# Methods

@@

We gathered a list of `r sum(methods$is_ti, na.rm=TRUE)` trajectory inference methods `r ref("table", "methods", anchor=TRUE)`, based on two existing lists found online [@davis_awesomesinglecelllistsoftware_2018,@gitter_singlecellpseudotimeoverviewalgorithms_2018] and by searching in literature for "trajectory inference" and "pseudotemporal ordering". We believe this to be the most complete list to data, but are welcome to include additional methods through e-mail or an issue on our github (https://github.com/dynverse/dynalysis). Methods were excluded from the evaluation based on several criteria: `r glue::collapse(glue::glue("({non_inclusion_reasons$footnote}) {non_inclusion_reasons$long}"), ", ")`. This resulted in the inclusion of `r sum(methods$evaluated)` methods in the evaluation (`r ref("table", "methods")`).

@@

We created a transparent scoring scheme to check the quality of each method (`r ref("table", "methods")`) and weighed each quality check by the number of times it was found in a list of
